---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CLix

<!-- badges: start -->
<!-- badges: end -->

The goal of CLix is to house a variety of functions that help in Alzheimer's Research in one convenient place for analysis.

## Installation

You can install the released version of CLix from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("CLix")
```

## Example

This is a basic example which shows you how to solve score a dataset using the developed CLix algorithm:

First load the data to be scored.

```{r first}
library(CLix)
library(tidyverse)

dat <- readRDS("data/example_data.rds") %>% 
  select(
    NPID, 
    AD.subtype, 
    CA1.NFT, 
    Subiculum.NFT, 
    Temporal.NFT, 
    Parietal.NFT, 
    Frontal.NFT
  ) %>% 
  rename(
    H1 = CA1.NFT, 
    H2 = Subiculum.NFT, 
    C1 = Temporal.NFT, 
    C2 = Parietal.NFT, 
    C3 = Frontal.NFT
  ) %>% 
  mutate(
    AD.subtype = factor(AD.subtype, levels = c("HpSp", "Typical", "Limbic"))
  )
```

Second use the CLix algorithm to score the new data against the nbM Flame Cohort (as the reference).
```{r, second}
res <- HpSp.scoring(dat = dat) %>% 
  select(NPID, HpSp.score.subtype, HpSp.score) %>% 
  mutate(
    HpSp.score.subtype = factor(HpSp.score.subtype, levels = c("HpSp", "Typical", "Limbic"))
  )
rescored_dat <- res %>% 
  inner_join(dat, by = "NPID")
```


Third compare the original AD subtype to the newly assigned AD subtype

```{r comparison, results='asis'}
arsenal::tableby(
  HpSp.score.subtype ~ AD.subtype, 
  data = rescored_dat, 
  total = F
) %>% 
  summary()
```
