---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Corticolimbic Index (CLix)

<!-- badges: start -->
<!-- badges: end -->

The goal of CLix is to personalize the Alzheimer's disease (AD) subtype algorithm by expressing it as a continuous numeric corticolimbic index (CLix). 


## Example

This is a basic example which shows you how to generate a score for a dataset using the developed CLix algorithm:

First load the data to be scored.

```{r first, include = FALSE}
library(CLix)
library(tidyverse)
```

```{r}
dat <- example_data %>% 
  select(
    NPID, 
    AD.subtype, 
    CA1.NFT, 
    Subiculum.NFT, 
    Temporal.NFT, 
    Parietal.NFT, 
    Frontal.NFT
  ) %>% 
  rename(
    H1 = CA1.NFT, 
    H2 = Subiculum.NFT, 
    C1 = Temporal.NFT, 
    C2 = Parietal.NFT, 
    C3 = Frontal.NFT
  ) %>% 
  mutate(
    AD.subtype = factor(AD.subtype, levels = c("HpSp", "Typical", "Limbic"))
  )
```

Second use the CLix algorithm to score the new data against the reference dataset. 

In this example, we are using our own FLAME-AD dataset as the reference dataset, in your own code, please replace NA with the name of your dataset for reference.dat.
```{r, second}
res <- CLix.scoring(dat = dat, reference.dat = NA) %>% 
  select(NPID, CLix.score.subtype, CLix.score) %>% 
  mutate(
    CLix.score.subtype = factor(CLix.score.subtype, levels = c("HpSp", "Typical", "Limbic"))
  )
rescored_dat <- res %>% 
  inner_join(dat, by = "NPID")
```

If you would like to replicate our findings using our reference dataset FLAME-AD, please reach out to us at peng.zhongwei\@mayo.edu or kwan.rain\@mayo.edu.

Third, we will compare the original AD subtype to the newly assigned AD subtype for our datasets.

```{r comparison, results='asis'}
arsenal::tableby(
  CLix.score.subtype ~ AD.subtype, 
  data = rescored_dat, 
  total = F
) %>% 
  summary()
```
